{\includegraphics[width=3cm, height=2.5cm]{Cran.jpg}} \\ \includegraphics[width=7cm, height=1cm]{TB.jpg} \\ {User Manual for TersectBrowser+}

### 2025-05-05 UserManual/UserMan.tex
Added licensing and contact

5. Licensing and contact

>>>>

5. Loading datasets

6. Licensing and contact
TersectBrowser+ is an application developed by Cranfield University. It is developed under the MIT license and incorporates components from JBrowse, which is released under the Apache License 2.0. The source code is freely available at [Github link]. The accompanying README contains additional information to setup and run TersectBrowser+. For future correspondance please contact Dr Tom Kurowski at: t.kurowski@cranfield.ac.uk.
